beautier: BEAUti for R

### 2017-12-20 article.tex
Improved references

\begin{table}[]
\centering
\begin{tabular}{ | l | l | }
\hline
\textbf{Name} & \textbf{Description} \\
\hline
\verb;create_beast2_input_file; & Creates a BEAST2 input file \\
\hline
\verb;create_gamma_site_model; & Create a gamma site model \\
\verb;create_gtr_site_model; & Create a GTR site model \\
\verb;create_hky_site_model; & Create an HKY site model \\
\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
\verb;create_tn93_site_model; & Create a TN93 site model \\
\hline
\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
\verb;create_strict_clock_model; & Create a strict clock model \\
\hline
\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
\verb;create_yule_tree_prior; & Create a Yule tree prior \\
\hline
\verb;create_beta_distr; & Create a beta distribution \\
\verb;create_exp_distr; & Create an exponential distribution \\
\verb;create_gamma_distr; & Create a gamma distribution \\
\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
\verb;create_laplace_distr; & Create a Laplace distribution \\
\verb;create_log_normal_distr; & Create a log-normal distribution \\
\verb;create_normal_distr; & Create a normal distribution \\
\verb;create_one_div_x_distr; & Create a 1/X distribution \\
\verb;create_poisson_distr; & Create a Poisson distribution \\
\verb;create_uniform_distr; & Create a uniform distribution \\
\hline
\end{tabular}
\caption{beautier's functions}
\label{tab:functions}
\end{table}

@@

\verb;beautier; has only parts of the functionality of BEAUti, yet
can be extended easily. \verb;beautier; , on the other hand, does allow for specifying
to use phylogenies of fixed crown age.

@@

This code will create a BEAST2 file with name '\verb;beast2.xml;',
using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
The default settings are, among others, to use a Jukes-Cantor site model, a strict clock,
and a Yule birth tree prior. Listing \ref{lis:simplest_example_explicit} shows how
to explicitly pick these settings:

@@

Coding style is the way statements are laid out, for example the placement of 
curly brackets. \verb;beautier; follows Hadley Wickham's style guide. 
Travis CI uses the \verb;lintr; \cite{lintr} package to comfirm this coding style
is used.

>>>>

\begin{table}[]
\centering
\begin{tabular}{ | l | l | }
\hline
\textbf{Name} & \textbf{Description} \\
\hline
\verb;create_beast2_input_file; & Creates a BEAST2 input file \\
\hline
\verb;create_gamma_site_model; & Create a gamma site model \\
\verb;create_gtr_site_model; & Create a GTR site model \\
\verb;create_hky_site_model; & Create an HKY site model \\
\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \cite{cantor1969mammalian} \\
\verb;create_tn93_site_model; & Create a TN93 site model \\
\hline
\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
\verb;create_strict_clock_model; & Create a strict clock model \\
\hline
\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
\verb;create_yule_tree_prior; & Create a Yule tree prior \\
\hline
\verb;create_beta_distr; & Create a beta distribution \\
\verb;create_exp_distr; & Create an exponential distribution \\
\verb;create_gamma_distr; & Create a gamma distribution \\
\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
\verb;create_laplace_distr; & Create a Laplace distribution \\
\verb;create_log_normal_distr; & Create a log-normal distribution \\
\verb;create_normal_distr; & Create a normal distribution \\
\verb;create_one_div_x_distr; & Create a 1/X distribution \\
\verb;create_poisson_distr; & Create a Poisson distribution \\
\verb;create_uniform_distr; & Create a uniform distribution \\
\hline
\end{tabular}
\caption{beautier's functions}
\label{tab:functions}
\end{table}

@@

\verb;beautier; has only parts of the functionality of BEAUti, yet
can be extended easily. \verb;beautier;, on the other hand, does allow for specifying
to use phylogenies of fixed crown age.

@@

This code will create a BEAST2 file with name '\verb;beast2.xml;',
using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
a strict clock, and a Yule birth tree prior. Listing \ref{lis:simplest_example_explicit} shows how
to explicitly pick these settings:

@@

Coding style is the way statements are laid out, for example the placement of 
curly brackets. \verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}. 
Travis CI uses the \verb;lintr; \cite{lintr} package to comfirm this coding style
is used.
